Cultural evolutionary dynamics with prestige bias

### 2022-12-29 ms/ms.tex
finish to edit intro

%\paragraph{Influence bias.}
Today, social media provides an easy way to estimate the social and cultural influence individuals have over others, and therefore may have an effect on decision making. Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
Influence can be easily estimated, so costs may be lower than estimating success. In some cases it could be a more accurate estimation as well.

Influence bias is a context-based, rather than a content-based bias--it does not depend on the phenotype but rather on the number of copiers that already copied each role-model. IT also differs from frequency biases such as conformity \citep{conformity}, which depend on the frequency of a trait in the population or in a sample of role-models rather than the social dynamics of copying.

Here, we define a model of cultural transmission with prestige bias that combines both success and influence biases, find analytic approximations for this model, and analyze its dynamics. We find approximations for the probability and time for fixation of a "successful" phenotype (i.e., that is favored by success bias). Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and influence bias play the role of natural selection and genetic drift, respectively.

>>>>

%\paragraph{Influence bias.}
Today, social media provides an easy way to estimate the social and cultural influence individuals have over others, and therefore may have an effect on decision making. Online social networks such as \emph{Facebook} and \emph{Instagram} are known to affect the influence of individuals \citep{social_influence,social_media,influence_analysis}, and specific marketing practices were invented to capitalize on this effect \citep{facebook_marketing}.
Here, we model such influence as an indirect bias in cultural transmission, in which the choice of a role-model depends on the choices made by other individuals that have already chosen a role-model. 
Importantly, influence may be easier and more accurate to estimate compared to success.

Influence bias is a context-based bias, rather than a content-based bias--it does not depend on the phenotype but rather on the number of copiers that already copied each role-model. It also differs from frequency biases such as conformity, which depend on the frequency of a trait in the population or in a sample of role-models rather than the social dynamics of copying.

Here, we define a stochastic model of cultural transmission with prestige bias that combines both success and influence biases, find analytic approximations for this model, and analyze its dynamics. We find approximations for the probability and time for fixation of a `successful' phenotype (i.e., that is favored by success bias). Comparing these approximations to Kimura's approximations for the fixation of a favorable allele \citep{kimura,kimura_average}, we demonstrate that success and influence bias play the role of natural selection and genetic drift, respectively.
